A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
Add introduction to classification section

This section presents an overiew of the usage of \eval in our corpus.
Previous work reported that 82\% of JavaScript-enabled web pages used
\eval~\cite{ecoop11}. The case for R is more striking with 100\% of the
programs using that \eval.\footnote{In this section, we combine calls to
  \c{eval}, \c{eval.parent}, \c{evalq} and \c{local}.}  This high number is
explained by the fact that the R implementation, its core packages, use
\eval extensively. In our analysis, we differentiate uses of \eval based on
where they originate from. A {\bf core} \eval is one that occurs in the code
of a core package.  A {\bf dependent} \eval is one that occurs in a package
that was included by the target package. An {\bf own} \eval is one that
occurs in the source code of the target package.

@@

>>>>

This section presents an overview of the usage of \eval in our corpus.
Previous work reported that 82\% of JavaScript-enabled web pages used
\eval~\cite{ecoop11}. The case for R is more striking with 100\% of the
programs using that \eval.\footnote{In this section, we combine calls to
  \c{eval}, \c{eval.parent}, \c{evalq} and \c{local}.}  This high number is
explained by the fact that the R implementation, its core packages, use
\eval extensively. In our analysis, we differentiate uses of \eval based on
where they originate from. A {\bf core} \eval is one that occurs in the code
of a core package.  A {\bf dependent} \eval is one that occurs in a package
that was included by the target package. An {\bf own} \eval is one that
occurs in the source code of the target package.

@@

This section presents the common patterns of \eval usage in our corpus. We
randomly selected 20 packages from the corpus and studied how they use eval.
We have grouped those uses in the following categories.
